---
title: 'R Lab 1 : R Basics'
author: "Saba Amin"
date: "8/21/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Basics Exercise - Solutions¶
# We will test you on a few topics:
# Basic Data Types
# Basic Arithmetic
# Vector
# Vector Operations
# Comparison operators
# Vector Selection and Indexing
# The exercises below should be straightforward if you've reviewed the lecture, don't expect something very challenging yet, this is more of a review to make sure you've understood everything so far! Later on exercises/projects will be more challenging (and a lot more fun!)

# Solve the following problems using R

#Ex 1: What is two to the power of five?
```{r}
2^5
```

#Ex 2: Create a vector called stock.prices with the following data points: 23,27,23,21,34
```{r}
stock.price <- c(23,27,23,21,34)
stock.price
```

#Ex 3: Assign names to the price data points relating to the day of the week, starting with Mon, Tue, Wed, etc...
```{r}
names(stock.price) <- c('Mon','Tues', 'Wed', 'Thur','Fri')
stock.price
```

#Ex 4: What was the average (mean) stock price for the week? (You may need to reference a built-in function)
```{r}
mean(stock.price)
```

#Ex 5: Create a vector called over.23 consisting of logicals that correspond to the days where the stock price was more than $23
```{r}
stock.price[stock.price > 23]
```

#Ex 6: Use the over.23 vector to filter out the stock.prices vector and only return the day and prices where the price was over $23
```{r}
stock.price[stock.price < 23]
```

#Ex 7: Use a built-in function to find the day the price was the highest
```{r}
max(stock.price)
```

#Ex 8: This didn't actually tell us the day! Only the max price, let's use a filter to grab the day!
```{r}
stock.price[stock.price == 34]
```

